Evolutionary rescue and reintroduction of resistant frogs allows recovery in the presence of a lethal fungal disease

### 2023-12-11 doc/manuscript/translocation.qmd

To identify important predictors of frog survival following translocation, we developed linear and multilevel models in a Bayesian framework.
Included predictor variables described characteristics of frogs, sites, and translocations (predictor variables: Bd load, sex, frog size, site elevation, winter severity in the year of translocation, winter severity in the year following translocation, donor population, day of year on which a translocation was conducted, and translocation order).
We used 1-year survival as a single metric of survival that was available for all translocated populations regardless of how many years of post-translocation data were available (range = 2--16).
Survival was rounded to integer values to produce a binomial outcome, and all models used a bernoulli family.
Group-level effects included site_id, translocation_id, or translocation_id nested within site_id.
We performed all analyses with the rstanarm package [@rstanarm2022] and R Statistical Software [v4.4.4, @rsoftware2022].
For all models, we used default, weakly informative priors, four chains, and 5000 iterations each for warmup and post-warmup.
We checked convergence of the MCMC algorithm using trace plots and Rhat, and evaluated model fit using leave-one-out ("LOO") cross-validation [@gelman2013; @gabry2019; @vehtari2016], as implemented by the loo package [@vehtari2022].

>>>>

To identify important predictors of frog survival following translocation, we used multilevel Bayesian models.
We included predictor variables to describe characteristics of frogs, sites, and translocations (predictor variables: Bd load, sex, frog size, site elevation, winter severity in the year of translocation, winter severity in the year following translocation, donor population, day of year on which a translocation was conducted, and translocation order).
We used 1-year post-translocation survival estimates from CMR models as the response, which was available for all translocated populations regardless of how many years of post-translocation data were available (range = 2--16).
Survival was rounded to integer values to produce a binary outcome, and modeled with a Bernoulli distribution.
Group-level effects included site_id, translocation_id, or translocation_id nested within site_id.
We performed all analyses with the rstanarm package [@rstanarm2022] and R Statistical Software [v4.4.4, @rsoftware2022].
For all models, we used default, weakly informative priors, four chains, and 5000 iterations each for warmup and post-warmup.
We checked MCMC convergence using trace plots and Rhat, and evaluated model fit using leave-one-out ("LOO") cross-validation [@gelman2013; @gabry2019; @vehtari2016], as implemented by the loo package [@vehtari2022].
